---
title: rCharts
subtitle: Interactive JS Charts from R
author: Ramnath Vaidyanathan
github: {user: ramnathv, repo: rChartsPerfAnalytics, branch: "gh-pages"}
framework: minimal
mode: selfcontained
widgets: [polycharts]
highlighter: highlight.js
hitheme: solarized_light
background: images/light_wool.png
assets:
  css: 
    - "http://fonts.googleapis.com/css?family=Open+Sans"
    - "http://fonts.googleapis.com/css?family=Open+Sans+Condensed:700"
---

```{r echo = F, message = F, cache = F}
opts_chunk$set(results = 'asis', comment = NA, message = F, tidy = F)
require(rCharts)
options(RCHART_WIDTH = 600, RCHART_HEIGHT = 400)
```

## Performance Analytics with rCharts and Slidify

This post illustrates how to get PerformanceAnalytics Charts using rCharts and Slidify. All the code here is courtesy [timelyportfolio](https://github.com/timelyportfolio/clickme_rCharts_test/). I have just done some minor refactoring.

Let us first load the require packages and set up the data we need.

```{r setupfunctions}
require(PerformanceAnalytics)
require(reshape2)
data(managers)
dat = managers[,c(1,8,9)]
```

### Process the Data

We need to process the data before we plot them. Here are a couple of helper functions to achieve that.

```{r}
xtsMelt <- function(xtsData,metric){
  df <- data.frame(index(xtsData),coredata(xtsData),stringsAsFactors=FALSE)
  df.melt <- melt(df,id.vars=1)
  df.melt <- data.frame(df.melt,rep(metric,NROW(df.melt)))
  #little unnecessary housekeeping
  df.melt <- df.melt[,c(1,2,4,3)]
  colnames(df.melt) <- c("date","indexname","metric","value")
  df.melt$date <- as.Date(df.melt$date)
  return(df.melt)
}
getCumul <- function(dat){
  data.cumul <- cumprod(1 + dat)
  data.melt <- xtsMelt(data.cumul, "CumulativeGrowth")
  i <- sapply(data.melt, is.factor)
  data.melt[i] <- lapply(data.melt[i], gsub, pattern="\\.", replacement="")
  #get date as text
  data.melt$date <- format(data.melt$date,"%Y-%m-%d")
  return(data.melt)
}
getDrawdowns <- function(dat) {
  data.drawdowns <- Drawdowns(dat)
  data.melt <- xtsMelt(data.drawdowns, "Drawdown")
  i <- sapply(data.melt, is.factor)
  data.melt[i] <- lapply(data.melt[i], gsub, pattern="\\.", replacement="")
  #get date as text
  data.melt$date <- format(data.melt$date,"%Y-%m-%d")  
  return(data.melt) 
}
```

## Plot It

Now that we have everything setup, it is time to get plotting.


```{r}
p1 <- rPlot(height = 400, value ~ date, data = getCumul(dat), 
  color = 'indexname', type = 'point', size = list(const=1)) 
p1$set( legendPosition = "top" )
p1$facet(type = "wrap",var = "metric", cols = 1,
 formatter="function(object) {return object.metric;}")
p1$print('chart1')
```

```{r}
p1 <- rPlot(height = 200, value ~ date, data = getDrawdowns(dat), 
 color = 'indexname', type = 'line', size = list(const = 1)) 
p1$set( legendPosition = "top" )
p1$facet(type = "wrap", var="metric", cols=1,
  formatter = "function(object) {return object.metric;}")
p1$print('chart2')
```

